cvx-flats

### 2020-04-17 neurips-20/cvx-flats.tex
New iteration of Thm 1 proof

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}

@@

\begin{definition}[Consistent]
	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ labeled examples.
	For all distributions $D$ over input and label spaces $\X \times\Y$, we say a loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if 
	\begin{align*}
		\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell(\psi \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
	\end{align*}
\end{definition}

@@

@@

@@

\begin{theorem}\label{thm:cvx-flats}
	Suppose we are given a finite elicitable property $\gamma$.
	Fix $p \in \simplex$, and let $r$ be a report such that $p \in \gamma_r$.  
	If there is no $(n - d - 1)$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals_+$ that indirectly elicits $\gamma$.
	Moreover, this must hold for all $p \in \simplex$ and $r \in \gamma(p)$.
\end{theorem}
\begin{proof}[Proof intuition]
	\jessie{BTW: $n$, or $\|p\|_0$?}
	We prove the contrapositive; if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.

	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e. $L$ indirectly elicits $\gamma$.
	Fix any $p \in \simplex$, and take any $r \in \gamma(p)$.
	We argue that there must be some $u \in \Gamma(p) \cap \reals^d$ such that $r = \psi(u)$, since $\Gamma(p) = \emptyset$ otherwise.
	We know that $r \in \gamma(p) \iff u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum by convex analysis results \jessie{And mild assumptions on the loss?}.

	Observe that the weighted Minkowski sum is in $d$-dimensional space as $L$ is defined on $\reals^d$.
	As $\partial L(u;p)$ is defined in $n$-dimensional space over $\simplex$, the flats of $L(u;p)$ are at least $(n-d-1)$-dimensional as the subgradient is in $d$-dimensional space, and the affineness of being a flat allows us to remove one additional dimension.
	Let $F$ be an $(n-d-1)$-dimensional flat to $L(u;p)$.
	For all $q \in F$, we must have $u \in \Gamma(q)$ since \jessie{JUSTIFICATION} there is a bijection from $F \in \partial L(u;p)$ to $\Gamma(p)$. Therefore, $q \in F \implies u \in \Gamma(q)$ as well.
	Therefore, we have $F \cap \simplex \subseteq \Gamma_u \subseteq \gamma_r$, where the latter follows from indirect elicitation.

@@

\begin{theorem}[Generalization to infinite outcomes?]
	Suppose we are given an elicitable property $\gamma$.
	Fix $p \in \simplex$, and let $r$ be a report such that $p \in \gamma_r$.  
	If there is no $\codim(\partial L(r;p))-1$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
	Moreover, this must hold for all $p \in \mathcal{P}$ and $r \in \gamma(p)$.
\end{theorem}

>>>>

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}

@@

\begin{definition}[Consistent: loss]
	Suppose $f_m : \X \to \R$ is the hypothesis function learned by minimizing empirical training loss over $m$ labeled examples.
	For all distributions $D$ over input and label spaces $\X \times\Y$, we say a loss and link $(L,\psi)$ \jessiet{change order of this sentence} are consistent with respect to an original loss $\ell$ if 
	\begin{align*}
		\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell(\psi \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
	\end{align*}
\end{definition}

\begin{definition}[Consistent: property]
\jessie{TODO}
\end{definition}
\jessiet{Excess risk definition on its own}

@@

\begin{remark}
	Either definition of consistency ties to indirect elicitation
\end{remark}

@@

\begin{definition}[Flat]
	A \emph{flat} $F$ of $\reals^n$ is an affine subspace of $\reals^n$.
\end{definition}

@@

\begin{theorem}\label{thm:cvx-flats}
	Suppose we are given a property $\gamma$.
	Fix $p \in \simplex$, and let $r$ be a report such that $p \in \gamma_r$.  
	If there is no $(n - d - 1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
	Moreover, this must hold for all $p \in \simplex$ and $r \in \gamma(p)$.
\end{theorem}
\begin{proof}[Proof intuition]
	\jessie{BTW: $n$, or $\|p\|_0$?}
	We prove the contrapositive; if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.

	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e. $L$ indirectly elicits $\gamma$.
	Fix any $p \in \simplex$, and take any $r \in \gamma(p)$.
	We argue that there must be some $u \in \Gamma(p) \subset \reals^d$ such that $r = \psi(u)$.
	We know that $r \in \gamma(p) \iff u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum by convex analysis results \jessie{And mild assumptions on the loss?}.

	Observe that the Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n]$ such that $\sum_y p_y x_y = \vec 0$.

	\jessiet{This next paragraph is mostly me spelling it out for myself}
	Observe that $F := \ker(W)$ is at most $(n-d-1)$ dimensions in probability space and contains $p$ by construction.
	Moreover, we must have $F \cap \simplex \subseteq \gamma_r$.
	To see this, consider $q \in F \cap \simplex$, but $q \not \in \gamma_r$.
	That would mean that $Wq = \vec 0$, which implies $\vec 0 \in \partial L(u;q)$, so $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.

		%%COMMENTED 04.16.20
%	Observe that the weighted Minkowski sum is in $d$-dimensional space as $L$ is defined on $\reals^d$.
%	As $\partial L(u;p)$ is defined in $n$-dimensional space over $\simplex$, the flats of $L(u;p)$ are at least $(n-d-1)$-dimensional as the subgradient is in $d$-dimensional space, and the affineness of being a flat allows us to remove one additional dimension.
%	Let $F$ be an $(n-d-1)$-dimensional flat to $L(u;p)$.
%	For all $q \in F$, we must have $u \in \Gamma(q)$ since \jessie{JUSTIFICATION} there is a bijection from $F \in \partial L(u;p)$ to $\Gamma(p)$. Therefore, $q \in F \implies u \in \Gamma(q)$ as well.
%	Therefore, we have $F \cap \simplex \subseteq \Gamma_u \subseteq \gamma_r$, where the latter follows from indirect elicitation.
%%end Commented 4.16.20

@@
